---
title: "BACS HW13"
author: '106070020'
date: "2021年5月21日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 Let’s visualize how weight and acceleration are related to mpg.

###(a) Let’s visualize how weight might moderate the relationship between acceleration and mpg:

####(i)Create two subsets of your data, one for light-weight cars (less than mean weight) and one for heavy cars (higher than the mean weight)
```{r}

cars <- read.table("C:/Users/eva/Desktop/作業 上課資料(清大)/大四下/BACS/HW11 BACS/auto-data.txt", header=F, na.strings = "?")
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight", 
                 "acceleration", "model_year", "origin", "car_name")
cars_log <- with(cars, data.frame(log(mpg), log(cylinders), log(displacement), log(horsepower), log(weight), log(acceleration), model_year, origin))
lmw<-mean(cars_log$log.weight.)
light <- subset(cars_log, log.weight.<lmw, na.action=na.exclude)
heavy <- subset(cars_log, log.weight.>lmw, na.action=na.exclude)

```

####(ii)Create a single scatter plot of acceleration vs. mpg, with different colors and/or shapes for light versus heavy cars
```{r}
#(ii)
with(light, plot(log.weight., log.mpg.,xlim=c(7.4,8.6),ylim=c(2,4), pch=19, col=2, main='single scatter plot of acceleration vs. mpg'))
with(heavy, points(log.weight., log.mpg., pch=18, col=4))
legend('topright', legend=c("light", "heavy"),
       col=c(2,4), pch=c(19,18), cex=0.75)
```

####(iii)Draw two slopes of acceleration-vs-mpg over the scatter plot: one slope for light cars and one slope for heavy cars (use different line styles)
```{r}
#(iii)
with(light, plot(log.weight., log.mpg.,xlim=c(7.4,8.6),ylim=c(2,4), pch=19, col=2, main='single scatter plot of acceleration vs. mpg'))
with(heavy, points(log.weight., log.mpg., pch=18, col=4))
abline(lm(log.mpg. ~ log.weight., data=light), col=2, lwd=2)
abline(lm(log.mpg. ~ log.weight., data=heavy), col=4, lwd=2, lty=2)
legend('topright', legend=c("light", "heavy"),
       col=c(2,4), pch=c(19,18), cex=0.75)
```

###(b)Report the full summaries of two separate regressions for light and heavy cars where log.mpg. is dependent on log.weight., log.acceleration., model_year and origin

```{r}
light<-na.omit(light)
heavy<-na.omit(heavy)
l<-lm(light$log.mpg.~light$log.weight.+light$log.acceleration.+light$model_year+factor(light$origin))
summary(l)
h<-lm(heavy$log.mpg.~heavy$log.weight.+heavy$log.acceleration.+heavy$model_year+factor(heavy$origin))
summary(h)
```

###(c)(not graded) Using your intuition only: What do you observe about light versus heavy cars so far?

***
> Both log.weight. and model_year have the significant effects on both light and heavy cars. While the log.acceleration. is only have a significant effect on light cars at 10% significance. 

## Question 2

###(a)(not graded) Between weight and acceleration ability, use your intuition and experience to state which variable might be a moderating versus independent variable, in affecting mileage.
```{r}
regr<- lm(log.mpg. ~ log.weight. + log.acceleration. + model_year +
            factor(origin),  data=cars_log)
summary(regr)
```

***
> In my opinion, log.acceleration. variable might be a moderating versus independent variable, in affecting mileage.


###(b)Use various regression models to model the possible moderation on log.mpg.:

####(i)Report a regression without any interaction terms
```{r}
regr<- lm(log.mpg. ~ log.weight. + log.acceleration. + model_year +
            factor(origin),  data=cars_log)
summary(regr)
```

####(ii)Report a regression with an interaction between weight and acceleration
```{r}
cars_log2<-with(cars_log, data.frame(log.mpg.,  log.weight.,  log.acceleration., model_year, origin))
regr_1<- lm(log.mpg. ~ log.weight. + log.acceleration. + model_year +
              factor(origin)+log.weight.*log.acceleration.,  data=cars_log2)
summary(regr_1)
cor(cbind(cars_log2,cars_log2$log.weight.*cars_log2$log.acceleration.))
```

####(iii)Report a regression with an interaction between weight and acceleration
```{r}
mlogw<-scale(cars_log2$log.weight.)
mloga<-scale(cars_log2$log.acceleration.)
regr_2<-lm(cars_log2$log.mpg. ~ mlogw + mloga +cars_log2$model_year +
             factor(cars_log2$origin)+ mlogw*mloga)
summary(regr_2)
```

####(iv)Report a regression with an orthogonalized interaction term
```{r}
logw_loga<-cars_log2$log.weight.*cars_log2$log.acceleration.
interaction_regr<-lm(logw_loga~cars_log2$log.weight.+cars_log2$log.acceleration.)
interaction_ortho<-interaction_regr$residuals
round(cor(cbind(cars_log2, interaction_ortho)),2)
summary(lm(log.mpg. ~ log.weight. + log.acceleration. + model_year +
              factor(origin)+interaction_ortho, data=cars_log2))
```

###(c)For each of the interaction term strategies above (raw, mean-centered, orthogonalized) what is the correlation between that interaction term and the two variables that you multiplied together?
```{r}
raw<-cor(cars_log2$log.weight., cars_log2$log.weight.*cars_log2$log.acceleration.)
raw
mc<-as.numeric(cor(mlogw, mlogw*mloga))
mc
oth<-round(cor(cbind(cars_log2$log.weight., interaction_ortho)),2)
oth

```
























