---
title: "BACS HW16"
author: '106070020'
date: "2021年6月11日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=F, warning=F}
library(seminr)
library(DiagrammeR)
library(semPlot)
sec<-read.csv("C:/Users/eva/Desktop/作業 上課資料(清大)/大四下/BACS/HW16 BACS/security_data_sem.csv", header = T)
dim(sec)
sec=as.data.frame(sec)
```


## Q1: Composite Path Models using PLS-PM
### (a)Create a PLS path model using SEMinR, with all the following characteristics:
####(i)Measurement model – all constructs are measured as composites:
```{r}
# Measurement Model
sec_mm<-constructs(
  composite("TRUST", multi_items("TRST", 1:4)),
  composite("SEC", multi_items("PSEC", 1:4)),
  composite("REP", multi_items("PREP", 1:4)),
  composite("INV", multi_items("PINV", 1:3)),
  composite("POL", multi_items("PPSS", 1:3)),
  composite("FAML", single_item("FAML1")),
  interaction_term(iv = "REP", moderator = "POL", method =  orthogonal))
```

####(ii)Structural Model – paths between constructs as shown in this causal model:
```{r}
sec_sm<-relationships(
  paths(from = c("REP", "INV", "POL","FAML", "REP*POL"), to = "SEC"),
  paths(from= "SEC",to= "TRUST"))
```

### (b)Show us the following results in table or figure formats:
####(i)Plot a figure of the estimated model
```{r}
sec_pls<-estimate_pls(
  data=sec,
  measurement_model = sec_mm,
  structural_model = sec_sm)
plot(sec_pls)
```

####(ii)Weights and loadings of composites
```{r}
sec_report<-summary(sec_pls)
sec_report$weights
sec_report$loadings
```

####(iii)Regression coefficients of paths between factors
```{r}
sec_report$paths
```


####(iv)Bootstrapped path coefficients: t-values, 95% CI
```{r message=F, warning=F}
boot_pls<-bootstrap_model(sec_pls,nboot= 1000)
boots_report<-summary(boot_pls)
boots_report$bootstrapped_paths
```


## Q2:Common-Factor Models using CB-SEM
###(a)Create a common factor model using SEMinR, with the following characteristics:

####(i)Either respecify all the constructs as being reflective(), or use the as.reflective() function to convert your earlier measurement model to being entirely reflective.
```{r}
sec_cf_mm<-as.reflective(sec_mm)
```

####(ii)Use the same structural model as before (you can just reuse it again!)
```{r message=F, warning=F}
sec_sm<-relationships(
  paths(from = c("REP", "INV", "POL","FAML", "REP*POL"), to = "SEC"),
  paths(from= "SEC",to= "TRUST"))
sec_cf_pls<-estimate_cbsem(
  data=sec,
  measurement_model = sec_cf_mm,
  structural_model = sec_sm)
```

###(b)Show us the following results in table or figure formats
####(i)Plot a figure of the estimated model (it will look different from your PLS model!)
```{r message=F, warning=F}
plot(sec_cf_pls)
```

####(ii)Loadings of composites
```{r}
sec_cf_report<-summary(sec_cf_pls)
sec_cf_report$loadings

```

####(iii)Regression coefficients of paths between factors, and their p-values
```{r}
sec_cf_report$paths
```




































